---
title: "<center> <h1>***SIZECONTEMO***</h1> </center>"
author: '[Antonio Schettino](https://www.researchgate.net/profile/Antonio_Schettino2 "Antonio Schettino")'
date: 2017-03-09
output:
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

In this project we will investigate the electrophysiological correlates of the combined processing of basic visual properties (i.e., size and contrast) and the emotional content of simple words. 

```{r setup_environment, include = FALSE}

# ## install packages
# install.packages("here")
# install.packages("knitr")
# install.packages("Rmisc")
# install.packages("yarrr")
# install.packages("fitdistrplus")
# install.packages("lme4")
# install.packages("car")
# install.packages("lsmeans")

## load packages
library(here)
library(knitr)
library(Rmisc)
library(yarrr)
library(fitdistrplus)
library(lme4)
library(car)
library(lsmeans)

set.seed(9001) # specify seed for RNG and ensure reproducible results (it's over 9000!)

# report output
options(width = 120, # change output width (for better printing)
        scipen = 999, # disable scientific notation (default: scipen = 0)
        digits = 3) # constrain output to 3 decimals

# chunk options
opts_chunk$set(
  warning = FALSE, # no package warnings
  message = FALSE, # no package messages
  fig.dim = c(10, 6) # width and height of all figures
  )

# 
# expname <- "SizeContEmo" # experiment name
# expphase <- "pilot" # experiment phase
# wd <- paste("D:/OneDrive - UGent/", expname, "/analysis/EEG/", expphase, "/", sep = "") # work directory
# setwd(wd) # set work directory

```

```{r main_data}

data.EEG.trial.all <- read.csv(here::here("EEG/pilot/data/pilot_trialEEG.csv"), header = TRUE) # load data

data.EEG.trial <- data.EEG.trial.all[data.EEG.trial.all$bin %in% c(1:8), ] # subset trials main experiment

data.EEG.trial$size <- # main effect of size
  revalue(
    factor(data.EEG.trial$bin),
    c(
      "1" = "large", "2" = "small", "3" = "large", "4" = "small",
      "5" = "large", "6" = "small", "7" = "large", "8" = "small"
    )
  )

data.EEG.trial$cont <- # main effect of contrast
  revalue(
    factor(data.EEG.trial$bin),
    c(
      "1" = "dark", "2" = "dark", "3" = "bright", "4" = "bright",
      "5" = "dark", "6" = "dark", "7" = "bright", "8" = "bright"
    )
  )

data.EEG.trial$emo <- # main effect of emotion
  revalue(
    factor(data.EEG.trial$bin),
    c(
      "1" = "negative", "2" = "negative", "3" = "negative", "4" = "negative",
      "5" = "neutral", "6" = "neutral", "7" = "neutral", "8" = "neutral"
    )
  )

data.EEG.trial$bin <- # recode bin variable
  revalue(
    factor(data.EEG.trial$bin),
    c(
      "1" = "negativeLargeDark", "2" = "negativeSmallDark", "3" = "negativeLargeBright", "4" = "negativeSmallBright",
      "5" = "neutralLargeDark", "6" = "neutralSmallDark", "7" = "neutralLargeBright", "8" = "neutralSmallBright"
    )
  )

data.EEG.trial <- within(data.EEG.trial, size <- relevel(size, ref = "large")) # reference size to large
data.EEG.trial <- within(data.EEG.trial, cont <- relevel(cont, ref = "dark")) # reference cont to dark
data.EEG.trial <- within(data.EEG.trial, emo <- relevel(emo, ref = "neutral")) # reference emo to neutral

```

The data we will use in this demo come from a pilot experiment (N = `r length(unique(data.EEG.trial$participant))`).   
   
We will first focus on the ERP data of the main task.   

<center> <h1>***MAIN TASK***</h1> </center>   

```{r main_normality}

# assess normality
ERPcomp <- factor(c("P1", "N1", "EPN", "LPP")) # ERP components

for (i in levels(ERPcomp)) { # loop through components
  
  for (j in levels(data.EEG.trial$bin)) { # loop through conditions
    
    tempdata <- data.EEG.trial[data.EEG.trial$bin == j, i] # subset current condition and ERP

    jpeg( # save as jpeg
      filename = here::here("EEG/pilot/graphs/normality", i, paste0(j, ".jpg")),
           width = 480, 
      height = 480, 
      units = "px", 
      quality = 100)
           
    plotdist(tempdata, histo = TRUE, demp = TRUE) # empirical density and cumulative distribution
    
    dev.off()
    
  }
  
}

```

Density plots (not shown in the output) suggest that the normal distribution is a parsimonious approximate description of the data.   
   
We will use linear mixed-effects models with random intercepts and fixed slopes. Models with random slopes have troubles converging, particularly on small datasets.
The random factor is participants, although in the future we will include items (i.e., the individual words) as well.

<center> <h1>*P1*</h1> </center>

```{r main_P1_graph}

# summarize data
summary.data.EEG.trial <- 
  summarySEwithin(
    data.EEG.trial, 
    "P1", 
    withinvars = c("size", "cont", "emo"), 
    idvar = "participant"
    )

summary.data.EEG.trial

# P1 graph
pirateplot(
  formula = P1 ~ emo + cont + size, # dependent~independent variables
  data = data.EEG.trial, # data frame
  main = "", # main title
  xlim = NULL, # x-axis: limits
  xlab = "", # x-axis: label
  ylim = c(-20, 20), # y-axis: limits
  ylab = expression(paste("amplitude (", mu, "V)")), # y-axis: label
  inf.method = "ci", # type of inference: 95% confidence intervals
  pal = "xmen" # color palette [see piratepal(palette="all")]
)

```  

We will compute the following models:   
   
1. null model
2. main effect of size
3. main effect of contrast
4. main effect of emotion
5. main effects of size and contrast
6. main effects of size and emotion
7. main effects of contrast and emotion
8. main effects of size, contrast, and emotion
9. size x contrast interaction
10. size x emotion interaction
11. contrast x emotion interaction
12. size x contrast x emotion interaction   
   
We will then compare them all using the Bayesian Infomation Criterion (BIC).

```{r main_P1_models}

### null model
P1.null.lmer.fixedslope <- lmer(P1 ~ 1 + (1 | participant), data = data.EEG.trial) # model
summary.P1.null.lmer.fixedslope <- summary(P1.null.lmer.fixedslope) # summary model

### main effect of size
P1.size.lmer.fixedslope <- lmer(P1 ~ size + (1 | participant), data = data.EEG.trial) # model
summary.P1.size.lmer.fixedslope <- summary(P1.size.lmer.fixedslope) # summary model
pvalue.P1.size.lmer.fixedslope <- Anova(P1.size.lmer.fixedslope) # calculate p-values
# contrasts
P1.size.lmer.fixedslope.contr <- lsmeans(P1.size.lmer.fixedslope, pairwise ~ size, adjust = "tukey")
# P1.size.lmer.fixedslope.contr$contrasts

### main effect of contrast
P1.cont.lmer.fixedslope <- lmer(P1 ~ cont + (1 | participant), data = data.EEG.trial) # model
summary.P1.cont.lmer.fixedslope <- summary(P1.cont.lmer.fixedslope) # summary model
pvalue.P1.cont.lmer.fixedslope <- Anova(P1.cont.lmer.fixedslope) # calculate p-values
# contrasts
P1.cont.lmer.fixedslope.contr <- lsmeans(P1.cont.lmer.fixedslope, pairwise ~ cont, adjust = "tukey")
# P1.cont.lmer.fixedslope.contr$contrasts

### main effect of emotion
P1.emo.lmer.fixedslope <- lmer(P1 ~ emo + (1 | participant), data = data.EEG.trial) # model
summary.P1.emo.lmer.fixedslope <- summary(P1.emo.lmer.fixedslope) # summary model
pvalue.P1.emo.lmer.fixedslope <- Anova(P1.emo.lmer.fixedslope) # calculate p-values
# contrasts
P1.emo.lmer.fixedslope.contr <- lsmeans(P1.emo.lmer.fixedslope, pairwise ~ emo, adjust = "tukey")
# P1.emo.lmer.fixedslope.contr$contrasts

### main effects of size and contrast
P1.sizecontmaineff.lmer.fixedslope <- lmer(P1 ~ size + cont + (1 | participant), data = data.EEG.trial) # model
summary.P1.sizecontmaineff.lmer.fixedslope <- summary(P1.sizecontmaineff.lmer.fixedslope) # summary model
pvalue.P1.sizecontmaineff.lmer.fixedslope <- Anova(P1.sizecontmaineff.lmer.fixedslope) # calculate p-values
# contrasts
P1.sizecontmaineff.lmer.fixedslope.contr <- lsmeans(P1.sizecontmaineff.lmer.fixedslope, pairwise ~ size + cont, adjust = "tukey")
# P1.sizecontmaineff.lmer.fixedslope.contr$contrasts

### main effects of size and emotion
P1.sizeemomaineff.lmer.fixedslope <- lmer(P1 ~ size + emo + (1 | participant), data = data.EEG.trial) # model
summary.P1.sizeemomaineff.lmer.fixedslope <- summary(P1.sizeemomaineff.lmer.fixedslope) # summary model
pvalue.P1.sizeemomaineff.lmer.fixedslope <- Anova(P1.sizeemomaineff.lmer.fixedslope) # calculate p-values
# contrasts
P1.sizeemomaineff.lmer.fixedslope.contr <- lsmeans(P1.sizeemomaineff.lmer.fixedslope, pairwise ~ size + emo, adjust = "tukey")
# P1.sizeemomaineff.lmer.fixedslope.contr$contrasts

### main effects of contrast and emotion
P1.contemomaineff.lmer.fixedslope <- lmer(P1 ~ cont + emo + (1 | participant), data = data.EEG.trial) # model
summary.P1.contemomaineff.lmer.fixedslope <- summary(P1.contemomaineff.lmer.fixedslope) # summary model
pvalue.P1.contemomaineff.lmer.fixedslope <- Anova(P1.contemomaineff.lmer.fixedslope) # calculate p-values
# contrasts
P1.contemomaineff.lmer.fixedslope.contr <- lsmeans(P1.contemomaineff.lmer.fixedslope, pairwise ~ cont + emo, adjust = "tukey")
# P1.contemomaineff.lmer.fixedslope.contr$contrasts

### main effects of size, contrast, and emotion
P1.allmaineff.lmer.fixedslope <- lmer(P1 ~ size + cont + emo + (1 | participant), data = data.EEG.trial) # model
summary.P1.allmaineff.lmer.fixedslope <- summary(P1.allmaineff.lmer.fixedslope) # summary model
pvalue.P1.allmaineff.lmer.fixedslope <- Anova(P1.allmaineff.lmer.fixedslope) # calculate p-values
# contrasts
P1.allmaineff.lmer.fixedslope.contr <- lsmeans(P1.allmaineff.lmer.fixedslope, pairwise ~ size + cont + emo, adjust = "tukey")
# P1.allmaineff.lmer.fixedslope.contr$contrasts

### size x contrast interaction
P1.sizecont.lmer.fixedslope <- lmer(P1 ~ size * cont + (1 | participant), data = data.EEG.trial) # model
summary.P1.sizecont.lmer.fixedslope <- summary(P1.sizecont.lmer.fixedslope) # summary model
pvalue.P1.sizecont.lmer.fixedslope <- Anova(P1.sizecont.lmer.fixedslope) # calculate p-values
# contrasts
P1.sizecont.lmer.fixedslope.contr <- lsmeans(P1.sizecont.lmer.fixedslope, pairwise ~ size * cont, adjust = "tukey")
# P1.sizecont.lmer.fixedslope.contr$contrasts

### size x emotion interaction
P1.sizeemo.lmer.fixedslope <- lmer(P1 ~ size * emo + (1 | participant), data = data.EEG.trial) # model
summary.P1.sizeemo.lmer.fixedslope <- summary(P1.sizeemo.lmer.fixedslope) # summary model
pvalue.P1.sizeemo.lmer.fixedslope <- Anova(P1.sizeemo.lmer.fixedslope) # calculate p-values
# contrasts
P1.sizeemo.lmer.fixedslope.contr <- lsmeans(P1.sizeemo.lmer.fixedslope, pairwise ~ size * emo, adjust = "tukey")
# P1.sizeemo.lmer.fixedslope.contr$contrasts

### contrast x emotion interaction
P1.contemo.lmer.fixedslope <- lmer(P1 ~ cont * emo + (1 | participant), data = data.EEG.trial) # model
summary.P1.contemo.lmer.fixedslope <- summary(P1.contemo.lmer.fixedslope) # summary model
pvalue.P1.contemo.lmer.fixedslope <- Anova(P1.contemo.lmer.fixedslope) # calculate p-values
# contrasts
P1.contemo.lmer.fixedslope.contr <- lsmeans(P1.contemo.lmer.fixedslope, pairwise ~ cont * emo, adjust = "tukey")
# P1.contemo.lmer.fixedslope.contr$contrasts

### size x contrast x emotion interaction
P1.sizecontemo.lmer.fixedslope <- lmer(P1 ~ size * cont * emo + (1 | participant), data = data.EEG.trial) # model
summary.P1.sizecontemo.lmer.fixedslope <- summary(P1.sizecontemo.lmer.fixedslope) # summary model
pvalue.P1.sizecontemo.lmer.fixedslope <- Anova(P1.sizecontemo.lmer.fixedslope) # calculate p-values
# contrasts
P1.sizecontemo.lmer.fixedslope.contr <- lsmeans(P1.sizecontemo.lmer.fixedslope, pairwise ~ size * cont * emo, adjust = "tukey")
# P1.sizecontemo.lmer.fixedslope.contr$contrasts

### model comparison via Bayesian Infomation Criterion (BIC)
P1.lmer.fixedslope.BIC <- BIC(P1.null.lmer.fixedslope, P1.size.lmer.fixedslope, P1.cont.lmer.fixedslope, P1.emo.lmer.fixedslope, P1.sizecontmaineff.lmer.fixedslope, P1.sizeemomaineff.lmer.fixedslope, P1.contemomaineff.lmer.fixedslope, P1.allmaineff.lmer.fixedslope, P1.sizecont.lmer.fixedslope, P1.sizeemo.lmer.fixedslope, P1.contemo.lmer.fixedslope, P1.sizecontemo.lmer.fixedslope)

# summary
compare.P1.lmer.fixedslope <- data.frame(model = c("null", "size", "contrast", "emotion", "size+contrast", "size+emotion", "contrast+emotion", "size+contrast+emotion", "size*contrast", "size*emotion", "contrast*emotion", "size*contrast*emotion"), BIC = P1.lmer.fixedslope.BIC$BIC)
compare.P1.lmer.fixedslope <- compare.P1.lmer.fixedslope[with(compare.P1.lmer.fixedslope, order(BIC)), ] # sort according to BIC (in ascending order)
compare.P1.lmer.fixedslope

```
   
The model to prefer should be `r compare.P1.lmer.fixedslope[1, 1]`. 

<center> <h1>*N1*</h1> </center>

```{r main_N1_graph}

# summarize data
summary.data.EEG.trial <-
  summarySEwithin(
    data.EEG.trial,
    "N1",
    withinvars = c("size", "cont", "emo"),
    idvar = "participant"
  )

summary.data.EEG.trial

# N1 graph
pirateplot(
  formula = N1 ~ emo + cont + size, # dependent~independent variables
  data = data.EEG.trial, # data frame
  main = "", # main title
  xlim = NULL, # x-axis: limits
  xlab = "", # x-axis: label
  ylim = c(-20, 20), # y-axis: limits
  ylab = expression(paste("amplitude (", mu, "V)")), # y-axis: label
  inf.method = "ci", # type of inference: 95% confidence intervals
  pal = "xmen" # color palette [see piratepal(palette="all")]
)

```  

```{r main_N1_models}

### null model
N1.null.lmer.fixedslope <- lmer(N1 ~ 1 + (1 | participant), data = data.EEG.trial) # model
summary.N1.null.lmer.fixedslope <- summary(N1.null.lmer.fixedslope) # summary model

### main effect of size
N1.size.lmer.fixedslope <- lmer(N1 ~ size + (1 | participant), data = data.EEG.trial) # model
summary.N1.size.lmer.fixedslope <- summary(N1.size.lmer.fixedslope) # summary model
pvalue.N1.size.lmer.fixedslope <- Anova(N1.size.lmer.fixedslope) # calculate p-values
# contrasts
N1.size.lmer.fixedslope.contr <- lsmeans(N1.size.lmer.fixedslope, pairwise ~ size, adjust = "tukey")
# N1.size.lmer.fixedslope.contr$contrasts

### main effect of contrast
N1.cont.lmer.fixedslope <- lmer(N1 ~ cont + (1 | participant), data = data.EEG.trial) # model
summary.N1.cont.lmer.fixedslope <- summary(N1.cont.lmer.fixedslope) # summary model
pvalue.N1.cont.lmer.fixedslope <- Anova(N1.cont.lmer.fixedslope) # calculate p-values
# contrasts
N1.cont.lmer.fixedslope.contr <- lsmeans(N1.cont.lmer.fixedslope, pairwise ~ cont, adjust = "tukey")
# N1.cont.lmer.fixedslope.contr$contrasts

### main effect of emotion
N1.emo.lmer.fixedslope <- lmer(N1 ~ emo + (1 | participant), data = data.EEG.trial) # model
summary.N1.emo.lmer.fixedslope <- summary(N1.emo.lmer.fixedslope) # summary model
pvalue.N1.emo.lmer.fixedslope <- Anova(N1.emo.lmer.fixedslope) # calculate p-values
# contrasts
N1.emo.lmer.fixedslope.contr <- lsmeans(N1.emo.lmer.fixedslope, pairwise ~ emo, adjust = "tukey")
# N1.emo.lmer.fixedslope.contr$contrasts

### main effects of size and contrast
N1.sizecontmaineff.lmer.fixedslope <- lmer(N1 ~ size + cont + (1 | participant), data = data.EEG.trial) # model
summary.N1.sizecontmaineff.lmer.fixedslope <- summary(N1.sizecontmaineff.lmer.fixedslope) # summary model
pvalue.N1.sizecontmaineff.lmer.fixedslope <- Anova(N1.sizecontmaineff.lmer.fixedslope) # calculate p-values
# contrasts
N1.sizecontmaineff.lmer.fixedslope.contr <- lsmeans(N1.sizecontmaineff.lmer.fixedslope, pairwise ~ size + cont, adjust = "tukey")
# N1.sizecontmaineff.lmer.fixedslope.contr$contrasts

### main effects of size and emotion
N1.sizeemomaineff.lmer.fixedslope <- lmer(N1 ~ size + emo + (1 | participant), data = data.EEG.trial) # model
summary.N1.sizeemomaineff.lmer.fixedslope <- summary(N1.sizeemomaineff.lmer.fixedslope) # summary model
pvalue.N1.sizeemomaineff.lmer.fixedslope <- Anova(N1.sizeemomaineff.lmer.fixedslope) # calculate p-values
# contrasts
N1.sizeemomaineff.lmer.fixedslope.contr <- lsmeans(N1.sizeemomaineff.lmer.fixedslope, pairwise ~ size + emo, adjust = "tukey")
# N1.sizeemomaineff.lmer.fixedslope.contr$contrasts

### main effects of contrast and emotion
N1.contemomaineff.lmer.fixedslope <- lmer(N1 ~ cont + emo + (1 | participant), data = data.EEG.trial) # model
summary.N1.contemomaineff.lmer.fixedslope <- summary(N1.contemomaineff.lmer.fixedslope) # summary model
pvalue.N1.contemomaineff.lmer.fixedslope <- Anova(N1.contemomaineff.lmer.fixedslope) # calculate p-values
# contrasts
N1.contemomaineff.lmer.fixedslope.contr <- lsmeans(N1.contemomaineff.lmer.fixedslope, pairwise ~ cont + emo, adjust = "tukey")
# N1.contemomaineff.lmer.fixedslope.contr$contrasts

### main effects of size, contrast, and emotion
N1.allmaineff.lmer.fixedslope <- lmer(N1 ~ size + cont + emo + (1 | participant), data = data.EEG.trial) # model
summary.N1.allmaineff.lmer.fixedslope <- summary(N1.allmaineff.lmer.fixedslope) # summary model
pvalue.N1.allmaineff.lmer.fixedslope <- Anova(N1.allmaineff.lmer.fixedslope) # calculate p-values
# contrasts
N1.allmaineff.lmer.fixedslope.contr <- lsmeans(N1.allmaineff.lmer.fixedslope, pairwise ~ size + cont + emo, adjust = "tukey")
# N1.allmaineff.lmer.fixedslope.contr$contrasts

### size x contrast interaction
N1.sizecont.lmer.fixedslope <- lmer(N1 ~ size * cont + (1 | participant), data = data.EEG.trial) # model
summary.N1.sizecont.lmer.fixedslope <- summary(N1.sizecont.lmer.fixedslope) # summary model
pvalue.N1.sizecont.lmer.fixedslope <- Anova(N1.sizecont.lmer.fixedslope) # calculate p-values
# contrasts
N1.sizecont.lmer.fixedslope.contr <- lsmeans(N1.sizecont.lmer.fixedslope, pairwise ~ size * cont, adjust = "tukey")
# N1.sizecont.lmer.fixedslope.contr$contrasts

### size x emotion interaction
N1.sizeemo.lmer.fixedslope <- lmer(N1 ~ size * emo + (1 | participant), data = data.EEG.trial) # model
summary.N1.sizeemo.lmer.fixedslope <- summary(N1.sizeemo.lmer.fixedslope) # summary model
pvalue.N1.sizeemo.lmer.fixedslope <- Anova(N1.sizeemo.lmer.fixedslope) # calculate p-values
# contrasts
N1.sizeemo.lmer.fixedslope.contr <- lsmeans(N1.sizeemo.lmer.fixedslope, pairwise ~ size * emo, adjust = "tukey")
# N1.sizeemo.lmer.fixedslope.contr$contrasts

### contrast x emotion interaction
N1.contemo.lmer.fixedslope <- lmer(N1 ~ cont * emo + (1 | participant), data = data.EEG.trial) # model
summary.N1.contemo.lmer.fixedslope <- summary(N1.contemo.lmer.fixedslope) # summary model
pvalue.N1.contemo.lmer.fixedslope <- Anova(N1.contemo.lmer.fixedslope) # calculate p-values
# contrasts
N1.contemo.lmer.fixedslope.contr <- lsmeans(N1.contemo.lmer.fixedslope, pairwise ~ cont * emo, adjust = "tukey")
# N1.contemo.lmer.fixedslope.contr$contrasts

### size x contrast x emotion interaction
N1.sizecontemo.lmer.fixedslope <- lmer(N1 ~ size * cont * emo + (1 | participant), data = data.EEG.trial) # model
summary.N1.sizecontemo.lmer.fixedslope <- summary(N1.sizecontemo.lmer.fixedslope) # summary model
pvalue.N1.sizecontemo.lmer.fixedslope <- Anova(N1.sizecontemo.lmer.fixedslope) # calculate p-values
# contrasts
N1.sizecontemo.lmer.fixedslope.contr <- lsmeans(N1.sizecontemo.lmer.fixedslope, pairwise ~ size * cont * emo, adjust = "tukey")
# N1.sizecontemo.lmer.fixedslope.contr$contrasts

### model comparison via Bayesian Infomation Criterion (BIC)
N1.lmer.fixedslope.BIC <- BIC(N1.null.lmer.fixedslope, N1.size.lmer.fixedslope, N1.cont.lmer.fixedslope, N1.emo.lmer.fixedslope, N1.sizecontmaineff.lmer.fixedslope, N1.sizeemomaineff.lmer.fixedslope, N1.contemomaineff.lmer.fixedslope, N1.allmaineff.lmer.fixedslope, N1.sizecont.lmer.fixedslope, N1.sizeemo.lmer.fixedslope, N1.contemo.lmer.fixedslope, N1.sizecontemo.lmer.fixedslope)

# summary
compare.N1.lmer.fixedslope <- data.frame(model = c("null", "size", "contrast", "emotion", "size+contrast", "size+emotion", "contrast+emotion", "size+contrast+emotion", "size*contrast", "size*emotion", "contrast*emotion", "size*contrast*emotion"), BIC = N1.lmer.fixedslope.BIC$BIC)
compare.N1.lmer.fixedslope <- compare.N1.lmer.fixedslope[with(compare.N1.lmer.fixedslope, order(BIC)), ] # sort according to BIC (in ascending order)
compare.N1.lmer.fixedslope

```
   
The model to prefer should be `r compare.N1.lmer.fixedslope[1, 1]`. 

<center> <h1>*EPN*</h1> </center>

```{r main_EPN_graph}

# summarize data
summary.data.EEG.trial <- 
  summarySEwithin(
    data.EEG.trial, 
    "EPN", 
    withinvars = c("size", "cont", "emo"), 
    idvar = "participant"
    )
summary.data.EEG.trial


# EPN graph
pirateplot(
  formula = EPN ~ emo + cont + size, # dependent~independent variables
  data = data.EEG.trial, # data frame
  main = "", # main title
  xlim = NULL, # x-axis: limits
  xlab = "", # x-axis: label
  ylim = c(-20, 20), # y-axis: limits
  ylab = expression(paste("amplitude (", mu, "V)")), # y-axis: label
  inf.method = "ci", # type of inference: 95% confidence intervals
  pal = "xmen" # color palette [see piratepal(palette="all")]
)

```  

```{r main_EPN_models}

### null model
EPN.null.lmer.fixedslope <- lmer(EPN ~ 1 + (1 | participant), data = data.EEG.trial) # model
summary.EPN.null.lmer.fixedslope <- summary(EPN.null.lmer.fixedslope) # summary model

### main effect of size
EPN.size.lmer.fixedslope <- lmer(EPN ~ size + (1 | participant), data = data.EEG.trial) # model
summary.EPN.size.lmer.fixedslope <- summary(EPN.size.lmer.fixedslope) # summary model
pvalue.EPN.size.lmer.fixedslope <- Anova(EPN.size.lmer.fixedslope) # calculate p-values
# contrasts
EPN.size.lmer.fixedslope.contr <- lsmeans(EPN.size.lmer.fixedslope, pairwise ~ size, adjust = "tukey")
# EPN.size.lmer.fixedslope.contr$contrasts

### main effect of contrast
EPN.cont.lmer.fixedslope <- lmer(EPN ~ cont + (1 | participant), data = data.EEG.trial) # model
summary.EPN.cont.lmer.fixedslope <- summary(EPN.cont.lmer.fixedslope) # summary model
pvalue.EPN.cont.lmer.fixedslope <- Anova(EPN.cont.lmer.fixedslope) # calculate p-values
# contrasts
EPN.cont.lmer.fixedslope.contr <- lsmeans(EPN.cont.lmer.fixedslope, pairwise ~ cont, adjust = "tukey")
# EPN.cont.lmer.fixedslope.contr$contrasts

### main effect of emotion
EPN.emo.lmer.fixedslope <- lmer(EPN ~ emo + (1 | participant), data = data.EEG.trial) # model
summary.EPN.emo.lmer.fixedslope <- summary(EPN.emo.lmer.fixedslope) # summary model
pvalue.EPN.emo.lmer.fixedslope <- Anova(EPN.emo.lmer.fixedslope) # calculate p-values
# contrasts
EPN.emo.lmer.fixedslope.contr <- lsmeans(EPN.emo.lmer.fixedslope, pairwise ~ emo, adjust = "tukey")
# EPN.emo.lmer.fixedslope.contr$contrasts

### main effects of size and contrast
EPN.sizecontmaineff.lmer.fixedslope <- lmer(EPN ~ size + cont + (1 | participant), data = data.EEG.trial) # model
summary.EPN.sizecontmaineff.lmer.fixedslope <- summary(EPN.sizecontmaineff.lmer.fixedslope) # summary model
pvalue.EPN.sizecontmaineff.lmer.fixedslope <- Anova(EPN.sizecontmaineff.lmer.fixedslope) # calculate p-values
# contrasts
EPN.sizecontmaineff.lmer.fixedslope.contr <- lsmeans(EPN.sizecontmaineff.lmer.fixedslope, pairwise ~ size + cont, adjust = "tukey")
# EPN.sizecontmaineff.lmer.fixedslope.contr$contrasts

### main effects of size and emotion
EPN.sizeemomaineff.lmer.fixedslope <- lmer(EPN ~ size + emo + (1 | participant), data = data.EEG.trial) # model
summary.EPN.sizeemomaineff.lmer.fixedslope <- summary(EPN.sizeemomaineff.lmer.fixedslope) # summary model
pvalue.EPN.sizeemomaineff.lmer.fixedslope <- Anova(EPN.sizeemomaineff.lmer.fixedslope) # calculate p-values
# contrasts
EPN.sizeemomaineff.lmer.fixedslope.contr <- lsmeans(EPN.sizeemomaineff.lmer.fixedslope, pairwise ~ size + emo, adjust = "tukey")
# EPN.sizeemomaineff.lmer.fixedslope.contr$contrasts

### main effects of contrast and emotion
EPN.contemomaineff.lmer.fixedslope <- lmer(EPN ~ cont + emo + (1 | participant), data = data.EEG.trial) # model
summary.EPN.contemomaineff.lmer.fixedslope <- summary(EPN.contemomaineff.lmer.fixedslope) # summary model
pvalue.EPN.contemomaineff.lmer.fixedslope <- Anova(EPN.contemomaineff.lmer.fixedslope) # calculate p-values
# contrasts
EPN.contemomaineff.lmer.fixedslope.contr <- lsmeans(EPN.contemomaineff.lmer.fixedslope, pairwise ~ cont + emo, adjust = "tukey")
# EPN.contemomaineff.lmer.fixedslope.contr$contrasts

### main effects of size, contrast, and emotion
EPN.allmaineff.lmer.fixedslope <- lmer(EPN ~ size + cont + emo + (1 | participant), data = data.EEG.trial) # model
summary.EPN.allmaineff.lmer.fixedslope <- summary(EPN.allmaineff.lmer.fixedslope) # summary model
pvalue.EPN.allmaineff.lmer.fixedslope <- Anova(EPN.allmaineff.lmer.fixedslope) # calculate p-values
# contrasts
EPN.allmaineff.lmer.fixedslope.contr <- lsmeans(EPN.allmaineff.lmer.fixedslope, pairwise ~ size + cont + emo, adjust = "tukey")
# EPN.allmaineff.lmer.fixedslope.contr$contrasts

### size x contrast interaction
EPN.sizecont.lmer.fixedslope <- lmer(EPN ~ size * cont + (1 | participant), data = data.EEG.trial) # model
summary.EPN.sizecont.lmer.fixedslope <- summary(EPN.sizecont.lmer.fixedslope) # summary model
pvalue.EPN.sizecont.lmer.fixedslope <- Anova(EPN.sizecont.lmer.fixedslope) # calculate p-values
# contrasts
EPN.sizecont.lmer.fixedslope.contr <- lsmeans(EPN.sizecont.lmer.fixedslope, pairwise ~ size * cont, adjust = "tukey")
# EPN.sizecont.lmer.fixedslope.contr$contrasts

### size x emotion interaction
EPN.sizeemo.lmer.fixedslope <- lmer(EPN ~ size * emo + (1 | participant), data = data.EEG.trial) # model
summary.EPN.sizeemo.lmer.fixedslope <- summary(EPN.sizeemo.lmer.fixedslope) # summary model
pvalue.EPN.sizeemo.lmer.fixedslope <- Anova(EPN.sizeemo.lmer.fixedslope) # calculate p-values
# contrasts
EPN.sizeemo.lmer.fixedslope.contr <- lsmeans(EPN.sizeemo.lmer.fixedslope, pairwise ~ size * emo, adjust = "tukey")
# EPN.sizeemo.lmer.fixedslope.contr$contrasts

### contrast x emotion interaction
EPN.contemo.lmer.fixedslope <- lmer(EPN ~ cont * emo + (1 | participant), data = data.EEG.trial) # model
summary.EPN.contemo.lmer.fixedslope <- summary(EPN.contemo.lmer.fixedslope) # summary model
pvalue.EPN.contemo.lmer.fixedslope <- Anova(EPN.contemo.lmer.fixedslope) # calculate p-values
# contrasts
EPN.contemo.lmer.fixedslope.contr <- lsmeans(EPN.contemo.lmer.fixedslope, pairwise ~ cont * emo, adjust = "tukey")
# EPN.contemo.lmer.fixedslope.contr$contrasts

### size x contrast x emotion interaction
EPN.sizecontemo.lmer.fixedslope <- lmer(EPN ~ size * cont * emo + (1 | participant), data = data.EEG.trial) # model
summary.EPN.sizecontemo.lmer.fixedslope <- summary(EPN.sizecontemo.lmer.fixedslope) # summary model
pvalue.EPN.sizecontemo.lmer.fixedslope <- Anova(EPN.sizecontemo.lmer.fixedslope) # calculate p-values
# contrasts
EPN.sizecontemo.lmer.fixedslope.contr <- lsmeans(EPN.sizecontemo.lmer.fixedslope, pairwise ~ size * cont * emo, adjust = "tukey")
# EPN.sizecontemo.lmer.fixedslope.contr$contrasts

### model comparison via Bayesian Infomation Criterion (BIC)
EPN.lmer.fixedslope.BIC <- BIC(EPN.null.lmer.fixedslope, EPN.size.lmer.fixedslope, EPN.cont.lmer.fixedslope, EPN.emo.lmer.fixedslope, EPN.sizecontmaineff.lmer.fixedslope, EPN.sizeemomaineff.lmer.fixedslope, EPN.contemomaineff.lmer.fixedslope, EPN.allmaineff.lmer.fixedslope, EPN.sizecont.lmer.fixedslope, EPN.sizeemo.lmer.fixedslope, EPN.contemo.lmer.fixedslope, EPN.sizecontemo.lmer.fixedslope)

# summary
compare.EPN.lmer.fixedslope <- data.frame(model = c("null", "size", "contrast", "emotion", "size+contrast", "size+emotion", "contrast+emotion", "size+contrast+emotion", "size*contrast", "size*emotion", "contrast*emotion", "size*contrast*emotion"), BIC = EPN.lmer.fixedslope.BIC$BIC)
compare.EPN.lmer.fixedslope <- compare.EPN.lmer.fixedslope[with(compare.EPN.lmer.fixedslope, order(BIC)), ] # sort according to BIC (in ascending order)
compare.EPN.lmer.fixedslope

```
   
The model to prefer should be `r compare.EPN.lmer.fixedslope[1, 1]`. 

<center> <h1>*LPP*</h1> </center>

```{r main_LPP_graph}

# summarize data
summary.data.EEG.trial <-
  summarySEwithin(
    data.EEG.trial,
    "LPP",
    withinvars = c("size", "cont", "emo"),
    idvar = "participant"
  )

summary.data.EEG.trial

# LPP graph
pirateplot(
  formula = LPP ~ emo + cont + size, # dependent~independent variables
  data = data.EEG.trial, # data frame
  main = "", # main title
  xlim = NULL, # x-axis: limits
  xlab = "", # x-axis: label
  ylim = c(-20, 20), # y-axis: limits
  ylab = expression(paste("amplitude (", mu, "V)")), # y-axis: label
  inf.method = "ci", # type of inference: 95% confidence intervals
  pal = "xmen" # color palette [see piratepal(palette="all")]
)

```  

```{r main_LPP_models}

### null model
LPP.null.lmer.fixedslope <- lmer(LPP ~ 1 + (1 | participant), data = data.EEG.trial) # model
summary.LPP.null.lmer.fixedslope <- summary(LPP.null.lmer.fixedslope) # summary model

### main effect of size
LPP.size.lmer.fixedslope <- lmer(LPP ~ size + (1 | participant), data = data.EEG.trial) # model
summary.LPP.size.lmer.fixedslope <- summary(LPP.size.lmer.fixedslope) # summary model
pvalue.LPP.size.lmer.fixedslope <- Anova(LPP.size.lmer.fixedslope) # calculate p-values
# contrasts
LPP.size.lmer.fixedslope.contr <- lsmeans(LPP.size.lmer.fixedslope, pairwise ~ size, adjust = "tukey")
# LPP.size.lmer.fixedslope.contr$contrasts

### main effect of contrast
LPP.cont.lmer.fixedslope <- lmer(LPP ~ cont + (1 | participant), data = data.EEG.trial) # model
summary.LPP.cont.lmer.fixedslope <- summary(LPP.cont.lmer.fixedslope) # summary model
pvalue.LPP.cont.lmer.fixedslope <- Anova(LPP.cont.lmer.fixedslope) # calculate p-values
# contrasts
LPP.cont.lmer.fixedslope.contr <- lsmeans(LPP.cont.lmer.fixedslope, pairwise ~ cont, adjust = "tukey")
# LPP.cont.lmer.fixedslope.contr$contrasts

### main effect of emotion
LPP.emo.lmer.fixedslope <- lmer(LPP ~ emo + (1 | participant), data = data.EEG.trial) # model
summary.LPP.emo.lmer.fixedslope <- summary(LPP.emo.lmer.fixedslope) # summary model
pvalue.LPP.emo.lmer.fixedslope <- Anova(LPP.emo.lmer.fixedslope) # calculate p-values
# contrasts
LPP.emo.lmer.fixedslope.contr <- lsmeans(LPP.emo.lmer.fixedslope, pairwise ~ emo, adjust = "tukey")
# LPP.emo.lmer.fixedslope.contr$contrasts

### main effects of size and contrast
LPP.sizecontmaineff.lmer.fixedslope <- lmer(LPP ~ size + cont + (1 | participant), data = data.EEG.trial) # model
summary.LPP.sizecontmaineff.lmer.fixedslope <- summary(LPP.sizecontmaineff.lmer.fixedslope) # summary model
pvalue.LPP.sizecontmaineff.lmer.fixedslope <- Anova(LPP.sizecontmaineff.lmer.fixedslope) # calculate p-values
# contrasts
LPP.sizecontmaineff.lmer.fixedslope.contr <- lsmeans(LPP.sizecontmaineff.lmer.fixedslope, pairwise ~ size + cont, adjust = "tukey")
# LPP.sizecontmaineff.lmer.fixedslope.contr$contrasts

### main effects of size and emotion
LPP.sizeemomaineff.lmer.fixedslope <- lmer(LPP ~ size + emo + (1 | participant), data = data.EEG.trial) # model
summary.LPP.sizeemomaineff.lmer.fixedslope <- summary(LPP.sizeemomaineff.lmer.fixedslope) # summary model
pvalue.LPP.sizeemomaineff.lmer.fixedslope <- Anova(LPP.sizeemomaineff.lmer.fixedslope) # calculate p-values
# contrasts
LPP.sizeemomaineff.lmer.fixedslope.contr <- lsmeans(LPP.sizeemomaineff.lmer.fixedslope, pairwise ~ size + emo, adjust = "tukey")
# LPP.sizeemomaineff.lmer.fixedslope.contr$contrasts

### main effects of contrast and emotion
LPP.contemomaineff.lmer.fixedslope <- lmer(LPP ~ cont + emo + (1 | participant), data = data.EEG.trial) # model
summary.LPP.contemomaineff.lmer.fixedslope <- summary(LPP.contemomaineff.lmer.fixedslope) # summary model
pvalue.LPP.contemomaineff.lmer.fixedslope <- Anova(LPP.contemomaineff.lmer.fixedslope) # calculate p-values
# contrasts
LPP.contemomaineff.lmer.fixedslope.contr <- lsmeans(LPP.contemomaineff.lmer.fixedslope, pairwise ~ cont + emo, adjust = "tukey")
# LPP.contemomaineff.lmer.fixedslope.contr$contrasts

### main effects of size, contrast, and emotion
LPP.allmaineff.lmer.fixedslope <- lmer(LPP ~ size + cont + emo + (1 | participant), data = data.EEG.trial) # model
summary.LPP.allmaineff.lmer.fixedslope <- summary(LPP.allmaineff.lmer.fixedslope) # summary model
pvalue.LPP.allmaineff.lmer.fixedslope <- Anova(LPP.allmaineff.lmer.fixedslope) # calculate p-values
# contrasts
LPP.allmaineff.lmer.fixedslope.contr <- lsmeans(LPP.allmaineff.lmer.fixedslope, pairwise ~ size + cont + emo, adjust = "tukey")
# LPP.allmaineff.lmer.fixedslope.contr$contrasts

### size x contrast interaction
LPP.sizecont.lmer.fixedslope <- lmer(LPP ~ size * cont + (1 | participant), data = data.EEG.trial) # model
summary.LPP.sizecont.lmer.fixedslope <- summary(LPP.sizecont.lmer.fixedslope) # summary model
pvalue.LPP.sizecont.lmer.fixedslope <- Anova(LPP.sizecont.lmer.fixedslope) # calculate p-values
# contrasts
LPP.sizecont.lmer.fixedslope.contr <- lsmeans(LPP.sizecont.lmer.fixedslope, pairwise ~ size * cont, adjust = "tukey")
# LPP.sizecont.lmer.fixedslope.contr$contrasts

### size x emotion interaction
LPP.sizeemo.lmer.fixedslope <- lmer(LPP ~ size * emo + (1 | participant), data = data.EEG.trial) # model
summary.LPP.sizeemo.lmer.fixedslope <- summary(LPP.sizeemo.lmer.fixedslope) # summary model
pvalue.LPP.sizeemo.lmer.fixedslope <- Anova(LPP.sizeemo.lmer.fixedslope) # calculate p-values
# contrasts
LPP.sizeemo.lmer.fixedslope.contr <- lsmeans(LPP.sizeemo.lmer.fixedslope, pairwise ~ size * emo, adjust = "tukey")
# LPP.sizeemo.lmer.fixedslope.contr$contrasts

### contrast x emotion interaction
LPP.contemo.lmer.fixedslope <- lmer(LPP ~ cont * emo + (1 | participant), data = data.EEG.trial) # model
summary.LPP.contemo.lmer.fixedslope <- summary(LPP.contemo.lmer.fixedslope) # summary model
pvalue.LPP.contemo.lmer.fixedslope <- Anova(LPP.contemo.lmer.fixedslope) # calculate p-values
# contrasts
LPP.contemo.lmer.fixedslope.contr <- lsmeans(LPP.contemo.lmer.fixedslope, pairwise ~ cont * emo, adjust = "tukey")
# LPP.contemo.lmer.fixedslope.contr$contrasts

### size x contrast x emotion interaction
LPP.sizecontemo.lmer.fixedslope <- lmer(LPP ~ size * cont * emo + (1 | participant), data = data.EEG.trial) # model
summary.LPP.sizecontemo.lmer.fixedslope <- summary(LPP.sizecontemo.lmer.fixedslope) # summary model
pvalue.LPP.sizecontemo.lmer.fixedslope <- Anova(LPP.sizecontemo.lmer.fixedslope) # calculate p-values
# contrasts
LPP.sizecontemo.lmer.fixedslope.contr <- lsmeans(LPP.sizecontemo.lmer.fixedslope, pairwise ~ size * cont * emo, adjust = "tukey")
# LPP.sizecontemo.lmer.fixedslope.contr$contrasts

### model comparison via Bayesian Infomation Criterion (BIC)
LPP.lmer.fixedslope.BIC <- BIC(LPP.null.lmer.fixedslope, LPP.size.lmer.fixedslope, LPP.cont.lmer.fixedslope, LPP.emo.lmer.fixedslope, LPP.sizecontmaineff.lmer.fixedslope, LPP.sizeemomaineff.lmer.fixedslope, LPP.contemomaineff.lmer.fixedslope, LPP.allmaineff.lmer.fixedslope, LPP.sizecont.lmer.fixedslope, LPP.sizeemo.lmer.fixedslope, LPP.contemo.lmer.fixedslope, LPP.sizecontemo.lmer.fixedslope)

# summary
compare.LPP.lmer.fixedslope <- data.frame(model = c("null", "size", "contrast", "emotion", "size+contrast", "size+emotion", "contrast+emotion", "size+contrast+emotion", "size*contrast", "size*emotion", "contrast*emotion", "size*contrast*emotion"), BIC = LPP.lmer.fixedslope.BIC$BIC)
compare.LPP.lmer.fixedslope <- compare.LPP.lmer.fixedslope[with(compare.LPP.lmer.fixedslope, order(BIC)), ] # sort according to BIC (in ascending order)
compare.LPP.lmer.fixedslope

```
   
The model to prefer should be `r compare.LPP.lmer.fixedslope[1, 1]`.
